XXX

### 2012-02-13 paper/engNERwiki.tex
Swapped the order of two subsections.
Just ****ing around...

The corpus is based on the Wikipedia snapshot as of XXX. The xml files were parsed with the XXX (Attila) parser. The raw text was tokenized with a modified version of the XXX sentence tokenizer in NLTK (CITE). The words were lemmatized with XXX and POS tagged by HunPos (CITE). Chunking was performed by HunChunk (CITE). Experiments have shown that HunPos obtains STAT f-score on the Brown corpus; HunChunk performs at around STAT, CITE?.

Though not included in the corpus, redirect pages can improve recall of the gold standard (XXX). 
% TODO: redirect redirect pages

@@

% 3. Training sentence extraction
%   a. only known links
%   b. title parts
%   c. parts of links mention earlier
%   d. date regexp
% 4. Test sentence extraction?
%   a. unknown links, no unlinked names
%   b. might be good for quality evaluation / recursive tagging (next paper?)
% 5. teaching the original DBpedia categories?

>>>>

The corpus is based on the Wikipedia snapshot as of XXX. The xml files were parsed with the XXX (Attila) parser. The raw text was tokenized with a modified version of the XXX sentence tokenizer in NLTK (CITE). The words were lemmatized with XXX and POS tagged with HunPos (CITE). Chunking was performed with HunChunk (CITE). Experiments have shown that HunPos obtains STAT f-score on the Brown corpus; HunChunk performs at around STAT, CITE?.

\subsubsection{Sentence selection}

A NER training corpus consists of sentences that contain "gold" quality information about the named entities (or lack thereof) occuring in them: XXX In order to achieve

The text in Wikipedia is 
Unknown entities might or might not be

whose validity is

Some  Resolving these links results in a STAT increase in recall.
Though not included in the corpus, redirect pages can improve recall of the gold standard (XXX). 
% TODO: redirect redirect pages

% 3. Training sentence extraction
%   a. only known links
%   b. title parts
%   c. parts of links mention earlier
%   d. date regexp
% recall+precision?

\subsubsection*{Filtering}

Some sentences that were selected by the process above

% 4. Test sentence extraction?
%   a. unknown links, no unlinked names
%   b. might be good for quality evaluation / recursive tagging (next paper?)
% 5. teaching the original DBpedia categories?

@@
